% main.tex — Critical Assessment of MULTING/IDM Framework
% Sergey Boyko · Ronin Institute · 2026-06-19
% NOT_VALIDATION · NOT_REFUTATION · OUR_RECONSTRUCTION
% Status: DRAFT · NOT_FOR_SUBMISSION

\documentclass[twocolumn,prd,amsmath,amssymb,floatfix]{revtex4-2}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{siunitx}

% Safety label macro
\newcommand{\reconstruction}{\textcolor{gray}{\small[OUR\_RECONSTRUCTION]}}
\newcommand{\notvalidation}{\textcolor{gray}{\small[NOT\_VALIDATION]}}

\begin{document}

\title{Systematic Assessment of the MULTING/IDM Gravitational Framework:\\
Confirmed Assets, Identified Gaps, and Independent Reconstructions}

\author{Sergey Boyko}
\affiliation{Ronin Institute for Independent Scholarship}
\email{sergeikuch80@gmail.com}
\date{\today}

\begin{abstract}
We present a systematic 36-point assessment of the MULTING/IDM preprint
(Buckholtz 2026, \texttt{preprints202511.0598.v6}), which proposes a
multipole-expansion extension of Newtonian gravity (MULTING) and an
isomer-based dark-matter framework (IDM). Using PDG 2024 constants, Planck 2018
cosmological parameters, and the MCXC/XMM galaxy cluster catalogs, we
independently verify the mass relations in Equations~(31) and~(32), quantify
the statistical preference for MULTING vs.\ $\Lambda$CDM in H(z) data, and
derive formal constraints on the IDM isomer count from the baryon density ratio
$\omega_\mathrm{DM}/\omega_b$.

We find: (1)~the empirical boson-mass relation [7:9:17] holds to $<0.05\%$
in mass units (the scale-free ratio $m_W/m_H = \sqrt{7/17}$ holds to $0.04\%$,
though per-boson the $W$ deviates by $3.8\sigma$ and $H$ by $1.1\sigma$ when
$Z$-anchored); stated parameter-free, the relation is consistent only with the
heavier (CDF-II/CMS) boson masses ($\chi^2 = 2.0$, $p = 0.36$) and excludes the
light/Standard-Model set ($\chi^2 = 39$), making it a falsifiable discriminant
on the $W$-mass anomaly. The fermion-gravity link (Eq.~32) holds at $0.17\sigma$
--- both empirical assets independent of MULTING/IDM cosmology; (2)~the fermion mass spectrum
(Eqs.~21--24) reproduces the muon mass to $0.47\%$ and quark geometric means
to $<0.31\%$ using PDG 2024 constants; (3)~the MULTING dipole term is
rendered negligible at cluster scales for the tabulated $\beta_d = 4.5$,
requiring $\beta_d \gtrsim 10^{3.2}$ for a 1\% observational signature ---
formally quantified via Birge Ratio $R_B = 15.9$ ($\beta_d$) and $R_B = 24.1$
($\beta_q$), both with $p < 10^{-4}$;
(4)~equal-mass $N=5$ IDM isomers are excluded at $5.67\sigma$ by Planck 2018,
but five isomers with $\bar{m} = 1.074\,m_p$ are Planck-compatible (EXP-N);
(5)~the $\Delta N_\mathrm{eff} > 100\sigma$ claim applies to a thermalized
mirror sector only; gravitational-only IDM gives $\Delta N_\mathrm{eff}
\lesssim 10^{-40}$, trivially within Planck bounds, though this eliminates
the dark baryogenesis mechanism (EXP-O);
(6)~the $H_\mathrm{FLRW}$ baseline used in Table~A1 is inconsistent with standard
$\Lambda$CDM (Planck MAE $= 120$~km\,s$^{-1}$\,Mpc$^{-1}$); a power-law
$H(z) = 54.07\,(1+z)^{0.884}$ fits the 11 Table~A1 points with
MAE $= 5.04$~km\,s$^{-1}$\,Mpc$^{-1}$.

These results neither validate nor refute MULTING/IDM, but map precisely which
components rest on verified foundations versus which require additional physics.
\end{abstract}

\maketitle

% ──────────────────────────────────────────────
\section{Introduction}
\label{sec:intro}
% ──────────────────────────────────────────────

The framework of Buckholtz~\cite{buckholtz2026} proposes a multipole-expansion
extension of Newtonian gravity (MULTING) in which galaxy clusters exert a
dipole force component $F_d$ and a quadrupole component $F_q$ that supplement
the monopole $F_m$, together modifying the Hubble expansion rate.
The preprint provides a table of predicted values (Table~A1) for
$H_\mathrm{MULT}(z)$ at 11 redshift points, derived from an AI-mediated
numerical procedure.

The six fundamental constants identified by Rees~\cite{rees1999} include
the ratio of electromagnetic to gravitational coupling strengths
$N \approx 10^{36}$ and the cosmological constant $\lambda \approx 0.7$.
MULTING/IDM addresses both: Eq.~(32) provides an empirical link between
$N$ and lepton masses ($0.17\sigma$, \S\ref{ssec:eq32}), while the MULTING
dipole term offers a mechanical alternative to $\lambda$ at first
cosmological perturbation order (\S\ref{sec:hz}).

A separate and timely test arises from the boson-mass relation Eq.~(31). Because
it fixes the ratios $m_W/m_Z$ and $m_H/m_Z$ with no free parameter, it speaks
directly to the unresolved $W$-mass tension --- the CDF-II~2022 value lies
$\sim 7\sigma$ above the Standard-Model expectation, while recent LHC
measurements favor the lighter, SM-consistent value. As we show
(\S\ref{ssec:bosons}), Eq.~(31) is statistically consistent only with the
heavier measurement set, turning a numerological-looking ratio into a concrete,
falsifiable prediction that forthcoming $W$-mass combinations will confirm or
exclude.

The principal challenge for external assessment is that the bridge connecting
cluster physical parameters ($k_A$, $r_A$, $D_{C:AB}$) to $H_\mathrm{MULT}$
is not derivable from first principles using standard cluster physics: the
tabulated $\varepsilon(z) \equiv (H_\mathrm{MULT}/H_\mathrm{FLRW})^2 - 1$
peaks at $z = 0.40$ and exhibits a secondary rise at $z = 8.50$, a
non-monotone shape inconsistent with virial-theorem cluster energetics (NR-004;
NR-008).  The phenomenological parameters $\beta_d$ and $\beta_q$ vary by
factors of $5.8\times$ and $95\times$ across three AI services queried in the
preprint, indicating that these parameters are not uniquely determined by the
stated procedure.

Our contribution is to separate what is independently verifiable from what
requires the author's undisclosed numerical procedure.
Section~\ref{sec:assets} verifies the mass relations (Eqs.~31, 32) against
PDG 2024.
Section~\ref{sec:hz} quantifies the statistical comparison of MULTING and
$\Lambda$CDM on H(z) data and identifies the $\beta$-rescaling gap.
Section~\ref{sec:idm} audits the IDM isomer-count prediction against Planck
2018 and standard dark-matter constraints.
All numerical results carry the label \reconstruction\ to distinguish our
independent reconstructions from author-attributed claims.

% ──────────────────────────────────────────────
\section{Verified Assets}
\label{sec:assets}
% ──────────────────────────────────────────────

\subsection{Boson Mass Relation (Eq.~31)}
\label{ssec:bosons}

The relation $m_W^2 : m_Z^2 : m_H^2 = 7:9:17$ (Eq.~31 of~\cite{buckholtz2026})
was tested against PDG 2024 masses~\cite{pdg2024}:
$m_W = 80.369 \pm 0.013$~GeV (PDG 2024 average, CDF-II 2022 excluded;
its inclusion drops the combination compatibility to $0.5\%$),
$m_Z = 91.1876 \pm 0.0021$~GeV,
$m_H = 125.20 \pm 0.11$~GeV (PDG 2024).

Using the $Z$ mass as anchor ($\lambda = m_Z^2/9 = 923.9$~GeV$^2$), the
predicted Higgs mass is $125.33$~GeV, agreeing with the measured value at
$1.14\sigma$.  The predicted $W$ mass is $80.420$~GeV, deviating by
$3.81\sigma$ from the PDG 2024 average.  Both predictions lie at the heavier
end of the currently discrepant measurements: the $W$ prediction agrees with
the CDF-II~2022 value ($80.4335 \pm 0.0094$) at $1.45\sigma$, and the $H$
prediction agrees with the CMS~2022 value ($125.35 \pm 0.15$) at $0.16\sigma$.
We emphasize that the per-boson significance is anchor-dependent: fixing the
scale $\lambda$ to any one boson renders that boson exact by construction
($0\sigma$), so the honest figure of merit is the \emph{largest} residual
across the three masses --- here the $W$ boson at $\approx 3.8\sigma$ --- not
the best-fitting one. We therefore report the relation as precise in mass
units ($<0.05\%$, below) but only marginally consistent in error-weighted
units, dominated by the $W$ tension.
\reconstruction

The anchor dependence is removed entirely by stating the relation in
\emph{scale-free} ratio form, which carries the same content without choosing
a reference boson:
\begin{equation}
    \frac{m_W}{m_H} = \sqrt{\tfrac{7}{17}} = 0.6417, \qquad
    \frac{m_W}{m_Z} = \sqrt{\tfrac{7}{9}} = 0.8819 .
\end{equation}
The ratio $m_W/m_H$ holds to $0.04\%$ against the PDG 2024 averages, and to
$0.003\%$ against the heavier $(m_W^\mathrm{CDF\text{-}II}, m_H^\mathrm{CMS})$
pair --- consistent with the observation above that the relation favors the
heavier end of both discrepant measurements. Because $m_W/m_H$ is independent
of the scale anchor, it is the cleaner observable: future $W$-mass combinations
provide a direct, anchor-free falsification test of Eq.~31.
\reconstruction

\paragraph{Preference statistic.}
Stated scale-free, Eq.~31 fixes the two ratios $m_W/m_Z=\sqrt{7/9}$ and
$m_H/m_Z=\sqrt{17/9}$ with \emph{zero} free parameters. We compute the 2-dof
$\chi^2$ of these predictions against three measurement scenarios that differ
only by the currently-discrepant $W$ and $H$ values
(Table~\ref{tab:c6pref}). The relation is statistically consistent
($\chi^2=2.0$, $p=0.36$) only with the \emph{heavy} set
(CDF-II~$m_W$ + CMS~$m_H$); the PDG-2024 average gives $\chi^2=15.6$
($p=4\times10^{-4}$) and the light set (CMS-24~$m_W$ + ATLAS~$m_H$) is excluded
at $\chi^2=39$. Eq.~31 therefore acts as a falsifiable discriminant favoring the
heavier, outlier measurements rather than the experimental consensus; it is a
bet, not evidence, and a future $W$ world-average converging below
$\sim 80.38$~GeV would exclude its error-weighted support at $>3\sigma$.
\reconstruction

\begin{table}[h]
\centering
\caption{7:9:17 zero-parameter $\chi^2$ (2 dof) by measurement scenario.}
\label{tab:c6pref}
\begin{tabular}{lccc}
\hline
Scenario & $\chi^2$ & $p$ & verdict \\
\hline
heavy (CDF-II $W$ + CMS $H$) & 2.0 & 0.36 & consistent \\
PDG-2024 average & 15.6 & $4\times10^{-4}$ & disfavored \\
light (CMS-24 $W$ + ATLAS $H$) & 39.0 & $<10^{-5}$ & excluded \\
\hline
\end{tabular}
\end{table}

A least-squares scale fit over all three masses simultaneously gives
$\lambda_\mathrm{LSQ} = 923.0$~GeV$^2$, with percentage deviations of
$-0.006\%$ ($W$), $+0.048\%$ ($Z$), $-0.012\%$ ($H$) in mass units ---
all below $0.05\%$, which is remarkably precise for a simple integer ratio
involving three independently measured bosons.
The ladder is specific to the electroweak bosons: the top quark gives
$(m_t/(m_Z/3))^2 = 32.3$, off the nearest integer ($32$) by $0.87\%$
($2.5\sigma$) --- an order of magnitude worse than the $W/Z/H$ fits --- so
Eq.~31 does not extend to the heavy-fermion sector.

\subsection{Fermion-Gravity Link (Eq.~32)}
\label{ssec:eq32}

The empirical relation
\begin{equation}
    \frac{4}{3}\left(\frac{m_\tau}{m_e}\right)^{12} = \frac{\alpha_\mathrm{EM}}{\alpha_G}
    \label{eq:c9}
\end{equation}
where $\alpha_G = G m_e^2 / (\hbar c)$, was evaluated using PDG 2024
constants~\cite{pdg2024}: $m_\tau = 1776.86 \pm 0.12$~MeV, $m_e = 0.51100$~MeV,
$\alpha_\mathrm{EM}^{-1} = 137.036$, $G = 6.674 \times 10^{-11}$~m$^3$~kg$^{-1}$~s$^{-2}$.

We find LHS/RHS~$= 1.000135$, corresponding to a $0.17\sigma$ agreement
dominated by the $m_\tau$ uncertainty.
\reconstruction

\paragraph{Formal uncertainty propagation.}
A first-order propagation through Eq.~(\ref{eq:c9}) using PDG 2024 and
CODATA 2018 uncertainties gives:
\begin{align}
  \sigma_\mathrm{LHS}(m_\tau) &= \tfrac{4}{3}\cdot 12\cdot
    \left(\frac{m_\tau}{m_e}\right)^{11}\!\frac{\sigma_{m_\tau}}{m_e}
    = 0.081\%\text{ of LHS} \notag \\
  \sigma_\mathrm{RHS}(G) &= \frac{\sigma_G}{G}\,\mathrm{RHS}
    = 0.0022\%\text{ of RHS} \notag \\
  \sigma_\mathrm{combined} &= 0.081\%\text{ of RHS};\quad
    |\mathrm{LHS}-\mathrm{RHS}|/\sigma = 0.167\sigma .
\end{align}
The dominant uncertainty is \emph{not} $G$ but $m_\tau$: the exponent 12
amplifies the $m_\tau$ contribution by a factor of $12^2 = 144$ relative to $G$'s
contribution at the same relative precision.
With the Belle~II target $\sigma_{m_\tau} = 0.01$~MeV~\cite{belleii2019},
the combined significance would rise to $1.90\sigma$ — an approaching but
not yet decisive test.
Partial derivatives verified against finite differences to $10^{-7}$ precision.
\reconstruction

\paragraph{Sensitivity to $G$ measurements.}
Different precision measurements of $G$ yield deviations of Eq.~(\ref{eq:c9})
ranging from $+0.0014\%$ \cite{luo2009} to $+0.032\%$ \cite{quinn2013},
all at sub-$0.4\sigma$ significance.  The spread among published $G$ values
($479$~ppm peak-to-peak across 10 experiments since 1982) exceeds the deviation
of Eq.~(\ref{eq:c9}) from equality ($135$~ppm with CODATA 2018~\cite{codata2018}),
implying that current $G$ precision \emph{prevents} a definitive test of whether
Eq.~(\ref{eq:c9}) is exact.  The value of $G$ that makes Eq.~(\ref{eq:c9})
exact is $G^* = 6.6734 \times 10^{-11}$~m$^3$\,kg$^{-1}$\,s$^{-2}$
(within the CODATA 2018 $1\sigma$ band); the Luo et al.~\cite{luo2009} measurement
($G = 6.67349\times10^{-11}$) is the closest published value, yielding
$+0.0014\%$ deviation.  A measurement at MICROSCOPE-class precision
($\sim\!1$~ppm in $G$) would still leave Eq.~(\ref{eq:c9}) limited by $m_\tau$,
not $G$, because the $m_\tau$ uncertainty contributes $0.081\%$ regardless of
$G$ precision.
\reconstruction

\paragraph{Context and status.}
Eq.~(\ref{eq:c9}) belongs to a recognized tradition of empirical relations
among lepton masses and fundamental constants --- the Koide
formula~\cite{sumino2009koide,xing2006koide,lima2006koide} and the
large-number coincidences first noted by Dirac~\cite{dirac1937}, recently
reviewed in the context of varying constants by Uzan~\cite{uzan2025constants}
and connected to mass ratios and gravity by Singh~\cite{singh2022massratios}.
Eq.~(\ref{eq:c9}) is distinct from these: whereas the Koide relation is a
permutation-symmetric sum rule over $\{e,\mu,\tau\}$, Eq.~(\ref{eq:c9}) ties
the single ratio $m_\tau/m_e$ to the electromagnetic-to-gravitational coupling
ratio $\alpha_\mathrm{EM}/\alpha_G$. Targeted searches of both indexed
open-access databases and the open web did not locate this specific relation,
though related lepton-mass relations (e.g.~Singh's octonionic
derivation~\cite{singh2022massratios}) are actively studied.
We stress that Eq.~(\ref{eq:c9}) is presented as an \emph{empirical regularity,
mechanism open}: unlike the Koide formula, which admits a family-gauge-symmetry
derivation~\cite{sumino2009koide}, no first-principles derivation of the
prefactor $4/3$ or the exponent $12$ is available here. In particular, we
tested and could not support a geometric ($S^3$ curvature-balance) origin for
the $4/3$ factor: writing $4/3 = (n+1)/n$ and $12 = n(n+1)$ at $n=3$ is one of
several hundred equally simple two-function relabelings consistent at $n=3$,
so the geometric reading carries no predictive content beyond the numerical
coincidence itself.
\reconstruction

\subsection{Fermion Mass Spectrum (Eqs.~21--24)}
\label{ssec:fermions}

The IDM mass formula predicts lepton masses as
$m_k/m_e = (m_\tau/m_e)^{(k + \sigma_k \delta)/3}$
with $k \in \{0,2,3\}$ for $\{e, \mu, \tau\}$, $\sigma_k \in \{0,-1,0\}$,
and $\delta = 0.03668$ (Eqs.~21--24 of~\cite{buckholtz2026}).
Using PDG 2024 masses ($m_e = 0.51100$, $m_\tau = 1776.86$~MeV), the electron
is reproduced exactly by construction; the muon prediction is $106.16$~MeV
vs.\ PDG $105.66$~MeV (deviation $0.47\%$).
The best-fit $\delta = 0.03841$ reduces this to $< 0.01\%$ for the muon
while preserving the tau anchor.
\reconstruction

For quarks, the formula is applied to geometric means of up/down-type pair masses.
The three predictions agree with PDG 2024 geometric means to $< 0.31\%$
(lightest: $\sqrt{m_u m_d} = 3.21$ vs.\ predicted $3.20$~MeV;
intermediate: $\sqrt{m_s m_c} = 344.7$ vs.\ $345.2$~MeV;
heavy: $\sqrt{m_b m_t} = 850$ vs.\ $851$~MeV).

The inflaton candidate (Eqs.~27--30 with $M'=T'=1$) predicts
$m_\mathrm{inflaton} = m_Z/3 = 30.396$~GeV.
No candidate particle at this mass has been reported at LEP or LHC;
this constitutes an open experimental prediction.

% ──────────────────────────────────────────────
\section{MULTING H(z) Test}
\label{sec:hz}
% ──────────────────────────────────────────────

\subsection{Statistical Comparison with $\Lambda$CDM}

We compare MULTING against the 27-point Moresco~\cite{moresco2022} cosmic-chronometer
compilation using 5-fold cross-validation on the polynomial model
$H(z) = A(1+z)^2 + B(1+z)^3 + C(1+z)^4$, which mirrors the MULTING
force-law sign pattern $(+,-,+)$ for (monopole, dipole, quadrupole).
\reconstruction

Across all 5 folds the coefficient $B$ is consistently negative
(cross-validation coefficient of variation $\mathrm{CV}(B) = 3\%$),
confirming that the sign pattern is a stable data-driven feature and not a
fitting artefact.
The $\Delta\mathrm{AIC}$ between the MULTING polynomial and flat $\Lambda$CDM
is $+0.74$ (MULTING disfavoured), below the distinguishability threshold
$|\Delta\mathrm{AIC}| = 2$.
Out-of-sample performance on held-out CC points gives
$\chi^2_\mathrm{test} = 1.80$ (MULTING) vs.\ $1.71$ ($\Lambda$CDM):
statistically indistinguishable.
\reconstruction

This confirms the analytic result of Blanchet \& Le Tiec~\cite{blanchet2008,blanchet2009}:
a dipolar dark-matter fluid is degenerate with $\Lambda$CDM at first
cosmological perturbation order.
Distinguishing MULTING from $\Lambda$CDM on H(z) data alone therefore requires
either second-order observables or a first-principles derivation of $\beta_d$
that yields $\varepsilon \gtrsim 1\%$ (see \S\ref{ssec:beta}).

\subsection{The $\beta$-Rescaling Gap}
\label{ssec:beta}

The dipole force fraction at cluster scale is
\begin{equation}
    \varepsilon \equiv \frac{F_d}{F_m} = \beta_d \frac{k_A}{M} \frac{r_A}{D},
    \label{eq:epsilon}
\end{equation}
where $k_A = E_\mathrm{ICM}/c^2$ is the cluster kinetic mass.
For a typical $T_X = 5$~keV, $M_{500} = 5\times10^{14}\,M_\odot$ cluster:
$k_A/M \approx 1.3 \times 10^{-6}$.

With the tabulated $\beta_d = 4.5$ (Table~A1 of~\cite{buckholtz2026}):
$\varepsilon \approx 6 \times 10^{-6}$ (negligible). An observational signature of
$\varepsilon \gtrsim 1\%$ requires $\beta_d \gtrsim 7.5 \times 10^3$.
The AI-service run reported $\beta_d \approx 2\times10^4$ (Gemini), which yields
$\varepsilon \approx 3\%$ (marginally non-negligible) but without a first-principles
derivation.
\reconstruction

To quantify the inter-service consistency of $\beta$ extractions, we apply the
Birge Ratio~\cite{birge1932} $R_B = \chi^2/(n-1)$ to three independent AI services
(Claude/NotebookLM: $\beta_d = 4.50$, $\beta_q = 18.0$;
Gemini: $4.25$, $8.10$; ChatGPT: $0.78$, $0.19$),
assuming a conservative relative uncertainty of $20\%$ per service.
We obtain $R_B = 15.9$ ($\chi^2 = 31.7$, $p < 10^{-4}$) for $\beta_d$ and
$R_B = 24.1$ ($\chi^2 = 48.3$, $p < 10^{-4}$) for $\beta_q$.
To achieve $R_B = 1$ (consistent services), a relative uncertainty of $80\%$
($\beta_d$) or $98\%$ ($\beta_q$) would be required --- far exceeding
the $\sim 20\%$ LLM extraction noise.
This \emph{Birge Ratio for AI Replication} (BRAI) confirms that $\beta$ values
are not uniquely determined by the stated procedure, consistent with the
author's own description of them as ``phenomenological computation''
whose derivation ``remains to be determined''.
\reconstruction

\subsection{H$_\mathrm{FLRW}$ Baseline Provenance}
\label{ssec:hflrw}

To assess whether the tabulated $H_\mathrm{FLRW}(z)$ values correspond to
standard $\Lambda$CDM, we fit the 11 Table~A1 redshifts with three candidates:
(i)~Planck 2018 flat $\Lambda$CDM ($H_0 = 67.4$, $\Omega_m = 0.315$);
(ii)~a power law $H(z) = A(1+z)^p$; and (iii)~a best-fit CC-data flat $\Lambda$CDM.
The Planck model yields MAE $= 120$~km\,s$^{-1}$\,Mpc$^{-1}$ --- a failure by
any standard.  The power-law gives $A = 54.07$, $p = 0.884$,
MAE $= 5.04$~km\,s$^{-1}$\,Mpc$^{-1}$ (best single-model fit).
The CC-data $\Lambda$CDM fit converges to $H_0 = 68.78$, $\Omega_m = 0.316$,
$\chi^2/\mathrm{dof} = 0.93$.
\reconstruction

These results establish that TJB's $H_\mathrm{FLRW}$ baseline is not
Planck 2018 $\Lambda$CDM.  All MULTING vs.\ $\Lambda$CDM comparisons
in this paper use the power-law proxy as the H$_\mathrm{FLRW}$ reference
pending author confirmation of the intended convention.

\textbf{Effect on $\varepsilon(z)$ claims (EXP-G).}
To quantify the impact of the baseline choice on the MULTING expansion claims,
we compute $\varepsilon_\mathrm{Planck}(z) \equiv (H_\mathrm{MULT}/H_\mathrm{Planck})^2 - 1$
using the Planck 2018 flat $\Lambda$CDM baseline ($H_0 = 67.4$, $\Omega_m = 0.315$,
arXiv:1807.06209 Table~2).
The $H_\mathrm{FLRW}$ values fall progressively below Planck: $-1.9\%$ at $z=0.06$,
$-10.6\%$ at $z=0.40$, $-15.0\%$ at $z=0.65$, $-20.7\%$ at $z=1.00$,
and $-64.1\%$ at $z=8.50$.
As a consequence, $\varepsilon_\mathrm{Planck}(z)$ changes sign near $z \approx 0.33$:
\begin{itemize}
  \item $z < 0.33$: $\varepsilon_\mathrm{Planck} > 0$ --- MULTING predicts \emph{more}
        expansion than Planck $\Lambda$CDM.  This low-$z$ excess is
        baseline-independent: it survives rebasing from the power-law proxy
        to true Planck $\Lambda$CDM (e.g.\ $\varepsilon_\mathrm{Planck}(0) =
        \varepsilon_\mathrm{FLRW}(0) = +0.113$ at $z=0$, where both baselines
        share the same $H_0$).
  \item $z > 0.33$: $\varepsilon_\mathrm{Planck} < 0$ --- MULTING predicts
        \emph{less} expansion than Planck $\Lambda$CDM.
        At $z = 0.65$: $\varepsilon_\mathrm{FLRW} = +0.213$ vs
        $\varepsilon_\mathrm{Planck} = -0.124$ (sign reversal of $0.337$).
        The positive $\varepsilon$ in Table~A1 at $z \ge 0.40$ reflects
        the below-Planck $H_\mathrm{FLRW}$ baseline, not an independent signal.
        Claims based on $\varepsilon(z)$ for $z > 0.4$ should be interpreted
        relative to the stated baseline.
\end{itemize}
\reconstruction

\subsection{Physical proxy for the dipole component}
\label{ssec:fsig8}

The $\Lambda$CDM model prediction for the growth rate observable,
$f\sigma_8(z) = \Omega_m(z)^{0.55}\,\sigma_8\,D(z)$
(Carroll--Press--Turner growth factor), is non-monotone: it rises from
$f\sigma_8 \approx 0.449$ at $z=0.06$ to a peak of $\approx 0.601$ at $z \approx 0.65$,
then falls to $\approx 0.259$ at $z=5$.
This bell-shaped curve correlates with $\varepsilon(z)$ at Pearson
$r = 0.851$ across $z \le 5$ ($n=10$ Table~A1 points).
The correlation captures a genuine \emph{shape match}: both are bell-peaked at
$z \sim 0.4$--$0.65$ ($r = 0.903$ on the rising half $z \le 0.65$;
$r = 0.958$ on the falling half $z \ge 0.65$).
Statistical significance: $p = 0.0018$ (two-tailed $t$-test, $df=8$);
95\% CI $= [0.48,\,0.96]$ (Fisher $z$-transform).
The correlation is robust across cosmological parameters:
$r \in [0.82, 0.87]$ on a $4\times4$ grid of
$\Omega_m \in [0.28, 0.32]$ and $\sigma_8 \in [0.77, 0.83]$.
\reconstruction

When tested against $n=11$ observed RSD $f\sigma_8$ measurements
(Beutler+2012, Blake+2012 WiggleZ, Samushia+2012 SDSS-LRG,
Howlett+2015 BOSS, de la Torre+2013 VIPERS, Okumura+2016 FastSound;
$z \in [0.07, 1.40]$; compiled from Kazantzidis \&\ Perivolaropoulos 2018,
arXiv:1803.01368, gold dataset), the correlation drops to $r = -0.084$
(EXP-D, [VERIFIED-REAL]), not significant ($p = 0.81$, $n=11$).
At the same $z$ values, the $\Lambda$CDM model gives $r = 0.778$ with $\varepsilon(z)$,
confirming that the gap is not a failure of the $\varepsilon$ shape but a
consequence of the $\sigma_8$ tension: observed $f\sigma_8$ values are
nearly flat ($\approx 0.38$--$0.51$), whereas the $\Lambda$CDM model
predicts a bell-peaked curve. \reconstruction
This absence of correlation with observed data may itself be informative:
both the MULTING $\varepsilon(z)$ deviation and the $\sigma_8$ tension
are largest near $z \sim 0.4$--$0.65$, suggesting a possible common
physical origin (open question, beyond BETA-1 HOLD).

This is consistent with MULTING's dipole term $F_d \propto k_A/r_P^2$
tracking the linear growth amplitude, pending $\beta_d$ derivation
(§\ref{ssec:beta}, open question Q2).

\textbf{Observational anchor caveat.}
The model $f\sigma_8(z)$ used in the correlation is a $\Lambda$CDM theoretical
prediction; observed RSD $f\sigma_8$ exist only up to $z \approx 2.33$
(DESI Lyman-$\alpha$, 2025, not yet validated for cosmological inference)
and $z \le 1.40$ for reliable galaxy-survey RSD.
All $f\sigma_8$ values at $z > 2$ in this analysis are model predictions,
not independent measurements.
\reconstruction

The full 11-point correlation yields $r = 0.775$, with the $z = 8.50$
point ($\varepsilon = 0.101 > \varepsilon_{z=5} = 0.048$, ratio $2.1\times$)
constituting an upward secondary bump.
This secondary feature at high redshift is consistent with the JWST-observed
excess of massive galaxies at $z \gtrsim 8$~\cite{tkachev2023}, which has been
attributed to a secondary enhancement in the dark-matter perturbation power
spectrum; the present framework offers an alternative geometric explanation via
the quadrupole term $F_q$.

\textbf{T-IDM (two-component structure, by physics-motivated exhaustion).}
Among 8 physics-motivated single-component families tested (virial $k_A(z)$,
merger-rate, log-Gaussian, Lognormal, $D^n H^m$ power products, and
merger-epoch $r_P$), no formula achieves Pearson $r > 0.85$ on all 11
$\varepsilon(z)$ points; the empirical ceiling is $r = 0.820$ for the
unconstrained $D^{5.5} H^{2.75}$ power product.
As an adversarial check, a 4-parameter Pad\'{e} rational function
$(a + bx)/(1 + cx + dx^2)$ with $x = 1+z$ achieves $r = 0.927$
on all 11 points~[\textit{OUR\_RECONSTRUCTION, verified numerically}].
However, the Pad\'{e} form carries no physical interpretation for the
secondary bump: its rational structure arises from fitting
degrees of freedom ($n/p = 2.75$), not from a physical mechanism.
This confirms that the 11-point $\varepsilon(z)$ curve requires a
non-monotone rational shape — consistent with MULTING's two-term
decomposition $F_\mathrm{oP} = F_m - F_d + F_q$, which provides a
physical identification of the two structural components (null-result
series NR-001 through NR-008, see supplementary).
\reconstruction

% ──────────────────────────────────────────────
\section{IDM Analysis}
\label{sec:idm}
% ──────────────────────────────────────────────

\subsection{Integer Isomer Count: $\chi^2$ Test}
\label{ssec:chi2}

The IDM prediction $\omega_\mathrm{DM} = N \omega_b$ (equal baryon asymmetry per
isomer) requires, from Planck 2018~\cite{planck2018}: $N_\mathrm{opt} =
\omega_\mathrm{DM}/\omega_b = 0.12011/0.022383 = 5.366$.

The nearest integer $N=5$ deviates by $5.67\sigma$, where the uncertainty
on the ratio $N_\mathrm{opt} = \omega_\mathrm{DM}/\omega_b$ is propagated
by the delta method:
\begin{equation}
\sigma_N = N_\mathrm{opt}\,\sqrt{\!\left(\frac{\sigma_{\omega_\mathrm{DM}}}
{\omega_\mathrm{DM}}\right)^{\!2}
+ \left(\frac{\sigma_{\omega_b}}{\omega_b}\right)^{\!2}}
= 5.366\times\sqrt{0.00999^2 + 0.00670^2} = 0.0646
\end{equation}
yielding $(N_\mathrm{opt} - 5)/\sigma_N = 5.67\sigma$\, ($\chi^2 = 33.5$,
assuming equal baryon asymmetry per isomer, $f \equiv 1$;
see caveat below).
\reconstruction

As an independent cross-check, the DESI DR1+CMB combination~\cite{desi2024vi}
gives $\omega_b = 0.02248 \pm 0.00013$ and $\Omega_m h^2 = 0.1418 \pm 0.0028$,
yielding $N_\mathrm{opt}^\mathrm{DESI} = 5.31 \pm 0.13$,
consistent with the Planck value at $0.46\sigma$ (note: $\omega_\mathrm{cdm}$ is
a derived quantity from the DESI+CMB joint fit; DESI BAO alone does not constrain
$\omega_b$ independently~\cite{desi2024vi}).
\reconstruction

\textbf{Assumption caveat ($f \equiv 1$).}
The $5.67\sigma$ exclusion of integer $N=5$ is conditional on all dark isomers
sharing the same baryon asymmetry per comoving volume as ordinary matter
($f \equiv \eta_\mathrm{dark}/\eta_\mathrm{SM} = 1$).
If the dark-sector baryon asymmetry differs by an $O(1)$ factor $f \neq 1$,
then $\omega_\mathrm{DM} = N\,f\,\omega_b$ and any integer $N$ maps to
a physically admissible $f$: for $N=6$, one obtains $f = 0.894$, a mild
$\sim\!11\%$ deficit requiring no exotic physics.
The analysis therefore constrains $N_\mathrm{opt}$ as a ratio assuming $f=1$;
distinguishing integer $N$ values requires independent constraints on
$\eta_\mathrm{dark}$ (open question, beyond current scope).
\reconstruction

\textbf{Mass-spectrum resolution (EXP-N).}
A second resolution arises if the five IDM isomers carry unequal masses.
Under equal baryon number per isomer ($f \equiv 1$), the IDM prediction
becomes $\omega_\mathrm{DM}/\omega_b = \sum_i (m_i/m_p)$.  The Planck 2018
central value $N_\mathrm{opt} = 5.369$ is reproduced exactly by five isomers
with common mass $\bar{m} = 1.074\,m_p$ --- a $7.4\%$ enhancement over the
proton mass, or by any five-isomer spectrum whose masses sum to
$5.369\,m_p$~\cite{rosa2022}.  Such a mass splitting is within the
$O(1)$ range expected for a dark QCD analogue; it does not require exotic
physics.  Distinguishing this scenario from $f \neq 1$ requires
independent measurement of the dark-sector baryon asymmetry.
\reconstruction

\subsection{Hot Dark Matter Problem}
\label{ssec:hdm}

In a mirror-sector IDM, dark neutrinos acquire masses comparable to their
SM counterparts ($m_{\nu,\mathrm{dark}} \sim m_\nu$) and decouple
relativistically.  Their free-streaming length $\lambda_\mathrm{fs}$
erases density fluctuations below cluster scales, inconsistent with
the observed matter power spectrum and Lyman-$\alpha$ forest
($\lambda_\mathrm{fs} \gtrsim 10$~Mpc for $m_\nu \lesssim 0.1$~eV).
This makes mirror-sector IDM a hot dark matter (HDM) candidate at the
neutrino mass scale, ruled out by structure formation.
\reconstruction

A gravitational-only coupling (dark sector thermally isolated from the SM
bath) suppresses this problem by allowing $T_\mathrm{dark} \ll T_\mathrm{SM}$,
but eliminates the dark baryogenesis mechanism that generates the dark baryon
asymmetry required for IDM.  This tension (E4) is internal to the framework
and does not have a resolution within the preprint.

\subsection{Self-Interaction Cross Section}
\label{ssec:sigma}

The Bullet Cluster merger constrains the dark matter self-interaction
cross section to $\sigma/m < 1.25$~cm$^2$/g at 68\% confidence~\cite{markevitch2006}.

A geometric estimate for the dark-nucleon self-interaction
gives $\sigma_\mathrm{nuc}/m \approx \pi r_n^2/m_p \approx 0.027$~cm$^2$/g
(using $r_n = 0.87$~fm, $m_p = 938.3$~MeV/$c^2$), which is within the
Bullet Cluster limit by a factor of $\approx 46$.
However, if dark isomers contain dark atoms (dark proton $+$ dark electron),
the atomic cross section at cluster velocities
($v_\mathrm{rel} \sim 10^3$~km$/$s, Bohr radius $a_0 = 0.529$~\AA)
gives $\sigma_\mathrm{atom}/m \approx \pi a_0^2 / m_p \approx 5 \times
10^7$~cm$^2$/g, exceeding the limit by seven orders of magnitude.
For bound dark nuclei with $A \ge 1$, the cross section scales as
$\sigma \propto A^{2/3}$ while $m \propto A$, giving
$\sigma/m \propto A^{-1/3}$, which falls below the 1.25 limit for $A \ge 1$.
\reconstruction

This analysis implies that IDM dark matter must consist of dark nuclei
(not free dark protons or dark atoms) to satisfy the Bullet Cluster constraint.
A mirror-sector IDM with dark electromagnetism can form dark atoms (violating
the limit); a gravitational-only coupling eliminates dark electromagnetism
and renders the nucleon-level cross section consistent, but again requires
abandoning the dark baryogenesis mechanism (see also §\ref{ssec:neff}).
\reconstruction

\subsection{Effective Relativistic Species ($N_\mathrm{eff}$)}
\label{ssec:neff}

Three regimes must be distinguished; they differ by tens of orders of magnitude
in $\Delta N_\mathrm{eff}$ (EXP-O \reconstruction).

\textbf{(i) Thermalized mirror sector.}
If the dark sector was in full thermal equilibrium with the SM bath
($T_\mathrm{dark} = T_\mathrm{SM}$ at BBN), each mirror-sector isomer
contributes relativistic degrees of freedom.  For a minimal mirror sector
(dark photons + dark neutrinos) $\Delta N_\mathrm{eff} \approx 22$;
including dark quarks and gluons yields $\Delta N_\mathrm{eff} \approx 37$--81;
for the full mirror SM ($g_\mathrm{eff} = 106.75$), $\Delta N_\mathrm{eff} = 106.8$.
The Planck 2018 bound $\Delta N_\mathrm{eff} < 0.284$ (95\% CL,
$N_\mathrm{eff} = 2.99 \pm 0.17$) is violated at $>100\sigma$ in all three
sub-cases.  This is the regime implicitly assumed by the $>100\sigma$ claim.

\textbf{(ii) Early-decoupling hidden sector.}
If the dark sector decoupled from the SM at temperature $T_\mathrm{dec}$,
subsequent SM entropy production dilutes the dark temperature.  The ratio today
satisfies $\xi \equiv T_\mathrm{dark}/T_{\nu} = (10.75/g_{*S}(T_\mathrm{dec}))^{1/3}$.
For $T_\mathrm{dec} \gtrsim 100$~GeV, $g_{*S} = 106.75$, $\xi = 0.465$, and
$\Delta N_\mathrm{eff} = g_\mathrm{eff,dark}\,\xi^4 \approx 0.047\,g_\mathrm{eff,dark}$:
Planck 2018 allows $g_\mathrm{dark} \lesssim 6$ at 95\% CL~\cite{chacko2015}.

\textbf{(iii) Gravitational-only production (IDM as stated).}
For a sector that \emph{never} thermalizes with the SM, production is via
gravitational particle production during reheating.  The effective temperature
scales as $T_\mathrm{dark}/T_\mathrm{SM} \sim (T_\mathrm{reh}/M_\mathrm{Pl})^{4/3}$
\cite{clery2021}, giving $T_\mathrm{dark}/T_\mathrm{SM} \lesssim 10^{-11}$ for
$T_\mathrm{reh} \lesssim 10^{10}$~GeV.  The resulting
$\Delta N_\mathrm{eff} \sim g_\mathrm{dark}(T_\mathrm{dark}/T_\nu)^4 \lesssim 10^{-40}$
is entirely negligible~\cite{clery2021,farina2018}.
The $>100\sigma$ exclusion therefore applies exclusively to the thermalized
mirror-sector interpretation (\textbf{i}), not to gravitational-only IDM.
\reconstruction

The binding tension for IDM is thus \emph{not} $\Delta N_\mathrm{eff}$
(trivially satisfied in regime~iii), but the internal conflict that
grav-only coupling removes the dark baryogenesis mechanism IDM requires
to predict its dark abundance (E4 tension, §\ref{ssec:hdm}).

% ──────────────────────────────────────────────
\section{Discussion}
\label{sec:discuss}
% ──────────────────────────────────────────────

\subsection{What Survives: H4 Empirical Relations}

Two results from this assessment are independent of the MULTING/IDM
cosmological framework and survive even if the framework itself is not
confirmed.

First, the fermion-gravity link (Eq.~32) holds at $0.17\sigma$ using PDG 2024
constants.  The relation $(4/3)(m_\tau/m_e)^{12} = \alpha_\mathrm{EM}/\alpha_G$
connects the strong gravitational coupling to the electromagnetic fine-structure
constant through lepton masses.  Its mechanism is unknown, but its numerical
precision is not easily dismissed as coincidence.

Second, the boson mass ratio $m_W^2:m_Z^2:m_H^2 \approx 7:9:17$ holds to
$<0.05\%$ in mass units across all three bosons in a least-squares fit, but
its error-weighted significance is anchor-dependent and dominated by the
$W$-boson residual ($\approx 3.8\sigma$ when $Z$-anchored, vs $1.14\sigma$ for
the Higgs); we therefore present it as a precise but not yet error-consistent
regularity. These ratios may encode a symmetry group that has yet to be identified.

Both results are independently testable as new PDG data accumulates (the
$m_\tau$ uncertainty currently dominates Eq.~32) and constitute H4 of the
original assessment framework.

\textbf{Uniqueness of $n=12$ in Eq.~(32).}
A power scan over integer exponents $n$ confirms that $n=12$ is the
\emph{unique} integer for which the relation
$(4/3)(m_\tau/m_e)^n = \alpha_\mathrm{EM}/\alpha_G$ holds within any
reasonable tolerance: adjacent integers give deviations of $\gtrsim 10^5\%$
($n=11$: $-99.97\%$; $n=13$: $+3.5\times10^5\%$). The best-fit
continuous exponent is $n_\mathrm{best} = 12.000$, confirming that $n=12$
is not an arbitrary choice but the unique integer where the ratio
$(m_\tau/m_e)^n$ crosses the target $\alpha_\mathrm{EM}/\alpha_G$.
A wider look-elsewhere scan over $5040$ combinations
($84$ rational prefactors $p/q$ with $q\le 6$ and $p\le 4q$, integer exponents
$1\le n\le 20$, and the three lepton mass pairs) yields a \emph{single}
match within $1\%$ of $\alpha_\mathrm{EM}/\alpha_G$, namely
$(4/3,\,n{=}12,\,m_\tau/m_e)$, and none within the $0.0135\%$ precision of
Eq.~(\ref{eq:c9}). The coincidence is therefore robust against the
multiple-comparisons inflation that weakens many numerical relations.
\reconstruction

\textbf{Algebraic origins of the coefficients.}
Independently of any physical model, the three integers appearing in
Eq.~(\ref{eq:c9}) --- the prefactor $4/3 = 36/27$, the exponent $12$, and
the implicit product $36$ --- correspond to dimensions of specific algebraic
objects in the exceptional-Lie-algebra chain $\mathrm{G}_2 \subset \mathrm{F}_4$:
(i) $12 = |\text{roots}(\mathrm{G}_2)|$, the total number of non-zero roots of
the Lie algebra $\mathrm{G}_2 = \mathrm{Aut}(\mathbb{O})$, where $\mathbb{O}$
denotes the octonions \cite{slansky1981}; independently, $12 = |W(\mathrm{G}_2)|$,
the order of the Weyl group of $\mathrm{G}_2$ --- two algebraic derivations of
the same integer;
(ii) $36 = \dim(\mathrm{SO}(9))$, and $27 = \dim(J_3(\mathbb{O}))$, the dimension
of the Albert algebra (exceptional Jordan algebra), giving $4/3 = 36/27$.
A null test over 2256 pairs from a pool of 48 algebraic integers (squares and
integer roots of dimensions of classical and exceptional Lie algebras)
confirms that finding both the ratio $4/3$ and the subset $\{36,27,12\}$ by
chance has probability $p\approx 1/37000$.
These connections are empirical observations, not derivations: they identify
the algebraic objects that \emph{count} the coefficients but do not explain
why those objects appear in the ratio $\alpha_\mathrm{EM}/\alpha_G$.
The $\mathrm{G}_2$ route is natural because $\mathrm{G}_2 = \mathrm{Aut}(\mathbb{O})$
and octonionic geometry underlies several approaches to Standard Model
structure~\cite{baezhuerta2010, todorov2018}; the specific connection
to $\alpha_G$ remains an open question.
A quark analogue --- replacing $m_\tau/m_e$ with quark mass ratios and the
exponent 12 with $\mathrm{E}_8$-motivated integers --- was tested and not found:
no quark pair satisfies an analogue of Eq.~(\ref{eq:c9}) within $5\%$ for
any exponent in the relevant range, confirming that the relation is
\emph{lepton-specific}.
\reconstruction

\textbf{$m_\tau$ value for an exact relation.}
If Eq.~(32) is taken as exact, it predicts
$m_\tau^\mathrm{exact} = 1776.840$~MeV,
which differs from the PDG 2024 value ($1776.86 \pm 0.12$~MeV) by
$-0.020$~MeV $= 0.17\sigma$.
Future Belle~II measurements targeting $\sigma_{m_\tau} < 0.01$~MeV
will provide a definitive test of whether Eq.~(32) is exact or approximate.
\reconstruction

\textbf{Joint Koide--Eq.~(32) constraint.}
The Koide formula
$(m_e + m_\mu + m_\tau)/(\sqrt{m_e}+\sqrt{m_\mu}+\sqrt{m_\tau})^2 = 2/3$
holds at $0.00092\%$ ($0.909\sigma$, PDG 2024) and is symmetric under all six
permutations of $\{m_e, m_\mu, m_\tau\}$ (i.e., $S_3$-invariant), involving
all three lepton generations.
Eq.~(\ref{eq:c9}) is distinct: it connects only the first and third
generations ($m_\tau/m_e$) to the gravitational coupling.
Inverting each relation for $m_\tau$:
\begin{align}
  m_\tau^\mathrm{Koide} &= 1776.969~\mathrm{MeV} \quad (+0.91\sigma\text{ from PDG}) ,\\
  m_\tau^\mathrm{Eq.32} &= 1776.840~\mathrm{MeV} \quad (-0.17\sigma\text{ from PDG}) .
\end{align}
The two ``exact'' predictions differ by $+0.129$~MeV ($+1.08\sigma$) ---
marginally compatible.  If both relations are simultaneously exact,
$m_\tau$ must lie within the window $[1776.840, 1776.969]$~MeV, which is
narrower than the current PDG uncertainty ($\pm 0.12$~MeV) and would be
resolved by the Belle~II target precision.  Under this joint constraint,
Newton's constant $G$ is determined from $\alpha_\mathrm{EM}$, $m_e$, and
$m_\mu$ alone, without $m_\tau$ as a free parameter ---
a non-trivial cross-constraint whose mechanism is unknown.
\reconstruction

\subsection{What Requires New Physics}

Three open questions require new physics or author disclosure to resolve.

\textit{MULTING Lagrangian (G3).}
No Lagrangian or action principle is provided for the multipole force
$F_\mathrm{oP}$.  Without a Lagrangian, the theory cannot be connected to
standard field-theoretic tools (renormalization, symmetry analysis, gravitational
waves) and Lorentz covariance cannot be verified.

\textit{IDM symmetry group (G4).}
The six IDM isomers are postulated by analogy with the SM, but the symmetry
group that distinguishes exactly six from other values of $N$ is not derived.
The $5.67\sigma$ tension with Planck 2018 ($N_\mathrm{opt} = 5.366$) may be
resolvable if the symmetry group predicts non-equal isomer masses or
baryon asymmetries.

\textbf{$S_3$ as a candidate group (hypothesis).}
The symmetric group $S_3$ (permutations of 3 objects, order 6) arises
independently in two contexts that converge on IDM's isomer count.
First, the Koide formula
$(m_e+m_\mu+m_\tau)/(\sqrt{m_e}+\sqrt{m_\mu}+\sqrt{m_\tau})^2 = 2/3$
is invariant under all six permutations of $\{m_e, m_\mu, m_\tau\}$
(i.e., $S_3$-symmetric by construction, verified independently~\cite{pdg2024}).
Second, under the regular (Cayley) representation of $S_3$ on itself,
the elements split canonically into $\{e\} \cup (S_3 \setminus \{e\})$:
one identity element (SESI, ordinary matter) and five non-identity elements
(MESI, dark matter), giving DM:OM $= 5{:}1$ as a group-theoretic consequence
rather than a counting postulate.
Additionally, the standard model's non-commutative geometry (Connes--Lott)
assigns $|S_3| = 6$ summands to the doubled algebra $\mathcal{A}_F \otimes
\mathcal{A}_F^\mathrm{op}$ and KO-dimension $= 6$, offering a third
independent path to the same integer.
This observation does not constitute a derivation; it identifies $S_3$ as a
candidate symmetry whose structure forbids $N=4$ or $N=7$ and predicts
the specific $1+5$ split without adjustable parameters.
Confirming this identification requires showing that IDM isomer quantum numbers
transform under the defining representation of $S_3$, which we record as an
open hypothesis.
\reconstruction

\textbf{$\Delta N_\mathrm{eff}$ constraint on IDM dark neutrinos (hypothesis).}
If each MESI isomer mirrors the SM, it contains three generations of dark
neutrinos, giving $N_{\nu,\mathrm{dark}} = 5 \times 3 = 15$ light fermionic
species.  When the dark sector is in thermal equilibrium with the SM at
temperature $T_\mathrm{dec}$ and subsequently decouples, SM entropy injections
(e.g., $e^+e^-$ annihilation, QCD transition) heat the photon bath relative
to the dark sector.  The residual dark-sector temperature ratio is
$\xi \equiv T_\mathrm{dark}/T_\gamma = (g_{*S}^\mathrm{today}/g_{*S}(T_\mathrm{dec}))^{1/3}$,
and the contribution to the effective number of relativistic species is
\begin{equation}
  \Delta N_\mathrm{eff} = N_{\nu,\mathrm{dark}}\,\xi^4\,\left(\tfrac{11}{4}\right)^{4/3}.
  \label{eq:dneff}
\end{equation}
At the SM maximum $g_{*S}(T_\mathrm{dec}) = 106.75$ (all SM particles in equilibrium
at $T > 200\,\mathrm{GeV}$), one finds $\xi = 0.332$ and
$\Delta N_\mathrm{eff} = 0.70$.
The Planck 2018 constraint $N_\mathrm{eff} = 2.99 \pm 0.17$ (68\% CL)
limits $\Delta N_\mathrm{eff} < 0.29$ (95\% CL), so 15 dark neutrinos are
\emph{ruled out} at the 2.5$\times$-excess level if the dark sector
thermalised within the SM.
The constraint requires either (A) dark-sector decoupling at $T_\mathrm{dec}$
where $g_{*S} > 210$, achievable in MSSM-like extensions with
$g_{*S}^\mathrm{MSSM} \approx 228$ at $T > 1\,\mathrm{TeV}$, or
(B) the absence of light dark neutrinos.
An alternative exit via massive dark neutrinos also fails: the minimum
mass for relativistic suppression implies $\Sigma m_{\nu,\mathrm{dark}} \gtrsim 1.3\,\mathrm{eV}$,
exceeding the Planck neutrino mass limit $\Sigma m_\nu < 0.12\,\mathrm{eV}$.
If the MSSM scenario (A) holds, the predicted $\Delta N_\mathrm{eff} \approx 0.26$
is above the Simons Observatory 2$\sigma$ detection threshold ($\sigma \approx 0.05$)
and will be tested by 2027.
\reconstruction

\textit{$\beta$ derivation from first principles (G2).}
The parameters $\beta_d$ and $\beta_q$ are fitted phenomenologically.
Their $5.8\times$ and $95\times$ spreads across AI services indicate
that the current procedure does not uniquely determine them.
A first-principles derivation linking $\beta$ to cluster microphysics
is the single most impactful open question for the MULTING H(z) test.

Note: Blanchet \& Le Tiec~\cite{blanchet2008, blanchet2009} demonstrated
that a dipolar dark-matter fluid is degenerate with $\Lambda$CDM at linear
perturbation order.  Our 5-fold cross-validation (§\ref{sec:hz}) confirms
this numerically: $\Delta\mathrm{AIC} = 0.74$, indistinguishable.
MULTING requires second-order predictions (non-geodesic cluster motions,
lensing anisotropy) to become observationally distinguishable.

\subsection{Forward-Looking Tests}
\label{sec:predictions}

The experiments reported here yield five falsifiable predictions, each
testable with facilities operating or under construction.
Table~\ref{tab:predictions} summarises the predictions, the required
observable, the instrument, and the approximate timeline.

\begin{table}[htb]
\caption{Falsifiable predictions from this analysis (OUR\_RECONSTRUCTION).
All predictions assume currently favoured cosmological parameters;
updates in DESI DR2 or Planck PR4 may shift central values.}
\label{tab:predictions}
\begin{ruledtabular}
\begin{tabular}{p{3.0cm}p{2.5cm}p{1.8cm}l}
Prediction & Observable & Instrument & Timeline \\
\hline
$m_\tau^\mathrm{exact} = 1776.840$~MeV if Eq.~(32) exact ($-0.17\sigma$ from PDG) &
$m_\tau$ to $\pm0.01$~MeV & Belle~II~\cite{belleii2019} & 2027 \\
$\Delta N_\mathrm{eff} \approx 0.26$ if IDM + MSSM decoupling ($g_{*S} \approx 228$) &
$\Delta N_\mathrm{eff}$ & Simons Obs. & 2026--2027 \\
$N_\mathrm{opt} = 5.31 \pm 0.05$--$0.09$ (3.3--5.9$\sigma$ from $N{=}5$) if $\sigma_{\omega_m}$ drops $\sqrt{2}$--$3\times$ from DR1 &
$\omega_m$, $\omega_b$ & DESI~DR2 & 2025--2026 \\
Non-geodesic cluster motions at $\gtrsim 2\sigma$ if $\beta_d \gtrsim 10^4$ &
$\sigma_v$, lensing anisotropy & Euclid~DR1 & 2026+ \\
$\varepsilon(z)$ secondary peak at $z \approx 8.5$ from $F_q$ if $\beta_q \gg \beta_d$ &
$f\sigma_8(z)$ at $z > 5$ & Future & 2030+ \\
\end{tabular}
\end{ruledtabular}
\end{table}

The most time-critical test is the Simons Observatory $\Delta N_\mathrm{eff}$
measurement.
If IDM's mirror sector decoupled from the SM at $T_\mathrm{dec}$ where
$g_{*S}(T_\mathrm{dec}) \approx 228$ (MSSM regime), the predicted
$\Delta N_\mathrm{eff} \approx 0.26$ lies above the Simons Observatory
$2\sigma$ detection threshold ($\sigma_{\Delta N_\mathrm{eff}} \approx 0.05$)
and below the Planck 2018 $95\%$ CL limit ($0.29$).
A non-detection by Simons Observatory would require $g_{*S}(T_\mathrm{dec}) > 300$,
pushing IDM's thermal decoupling to scales above the MSSM.
\reconstruction

\subsection{Assessment Summary}

\begin{table}[htb]
\caption{36-point assessment summary (OUR\_RECONSTRUCTION)}
\label{tab:summary}
\begin{ruledtabular}
\begin{tabular}{lll}
\hline
Component & Status & Evidence \\
\hline
Eq.~31 (7:9:17 bosons) & $\triangle$ $m_W/m_H$ at $0.04\%$; $1.14\sigma$ (H), $3.8\sigma$ (W) & PDG 2024 \\
Eq.~32 (fermion-gravity) & $\checkmark$ $0.17\sigma$ & PDG 2024 \\
Eqs.~21--24 (fermion masses) & $\checkmark$ muon $0.47\%$, quarks $<0.31\%$ & PDG 2024 \\
Inflaton $m_Z/3 = 30.4$~GeV & ? undetected & LEP/LHC null \\
Cassini constraint & $\checkmark$ pass & $\varepsilon \sim 10^{-19}$ \\
H(z) correlation & $\triangle$ $\Delta\mathrm{AIC}{=}{+}0.74$ & 27 Moresco CC \\
$H_\mathrm{FLRW}$ provenance & $\times$ not Planck & MAE $120$ vs $5$ \\
$\beta_d = 4.5$ observability & $\times$ negligible & $k_A/M$ calc \\
$\beta$ BRAI & $\times$ $R_B{=}15.9/24.1$ ($p{<}10^{-4}$) & 3 AI services \\
IDM $N=5$ equal-mass & $\times$ $5.67\sigma$ & Planck 2018 (EXP-N) \\
IDM $N=5$ unequal-mass & $\triangle$ $\bar{m}=1.074\,m_p$ & mass-spectrum resolution \\
IDM CDM viability & $\times$ killed & HDM $+$ E4 tension \\
$f\sigma_8$ dipole proxy & $\triangle$ $r{=}0.851$ ($n{=}10$, $z{\le}5$) & Table A1 $+$ $\Lambda$CDM \\
Secondary $z{=}8.5$ bump & $\triangle$ structural & Two-component $\varepsilon$ \\
MULTING Lagrangian & ? open & Future work \\
6-isomer symmetry & ? open & Future work \\
\hline
\end{tabular}
\end{ruledtabular}
\end{table}

% ──────────────────────────────────────────────
\section{Conclusions}
\label{sec:conclusions}
% ──────────────────────────────────────────────

We have conducted a systematic 36-point assessment of the MULTING/IDM
framework~\cite{buckholtz2026}, focusing on components that are independently
verifiable with public data and PDG constants.

Several results survive independent scrutiny without requiring the author's
undisclosed numerical procedure.
The fermion-gravity link (Eq.~32) holds at $0.17\sigma$ (PDG 2024),
and the boson mass ratio [7:9:17] holds at $<0.05\%$ in mass units
with the scale-free ratio $m_W/m_H = \sqrt{7/17}$ precise to $0.04\%$.
The fermion mass spectrum (Eqs.~21--24) reproduces the muon mass to $0.47\%$
and quark geometric means to $<0.31\%$.
These H4 results are non-trivial empirical regularities regardless of the
status of MULTING cosmology.

A key methodological finding is that the H$_\mathrm{FLRW}$ baseline in
Table~A1 is inconsistent with standard Planck 2018 $\Lambda$CDM
(MAE $= 120$~km\,s$^{-1}$\,Mpc$^{-1}$); a power-law $H(z)=54.07(1+z)^{0.884}$
fits the same 11 points with MAE $= 5.04$~km\,s$^{-1}$\,Mpc$^{-1}$.
This means that comparisons of MULTING vs.\ ``standard cosmology'' must
specify which H$_\mathrm{FLRW}$ convention is intended.

The IDM cosmological predictions face two structural constraints, with a
third that depends on the coupling assumption.
First, $N=5$ \emph{equal-mass} isomers are excluded at $5.67\sigma$ by Planck
2018; however, five isomers with a common mass $\bar{m} = 1.074\,m_p$ exactly
reproduce the observed $\omega_\mathrm{DM}/\omega_b = 5.369$, converting the
exclusion into a mass-spectrum constraint (EXP-N).
Second, the $\Delta N_\mathrm{eff}$ bound depends critically on the dark-sector
coupling: a fully thermalized mirror sector gives $\Delta N_\mathrm{eff} = 106.8$,
excluded at $>100\sigma$; a gravitational-only sector (IDM as stated) gives
$\Delta N_\mathrm{eff} \lesssim 10^{-40}$, entirely within Planck bounds (EXP-O).
The ``$>100\sigma$'' characterization applies only to the thermalized regime
and is a \emph{misclassification} when applied to grav-only IDM~\cite{clery2021}.
A massive-neutrino escape route for the thermalized case fails because it implies
$\Sigma m_{\nu,\mathrm{dark}} \geq 1.3$~eV $\gg$ the Planck mass limit
$0.12$~eV.
The minimal viable scenario requires BSM physics above the electroweak scale
($g_{*S}(T_\mathrm{dec}) > 210$); MSSM-like extensions predict
$\Delta N_\mathrm{eff} \approx 0.26$, within Planck bounds but detectable by
Simons Observatory by 2027 (Table~\ref{tab:predictions}).
Third, a gravitational-only coupling that would suppress $\Delta N_\mathrm{eff}$
eliminates the dark baryogenesis mechanism (E4 internal tension).

The MULTING H(z) test is currently limited by the $\beta$-rescaling gap:
the tabulated $\beta_d = 4.5$ gives a negligible dipole signal
($\varepsilon \sim 10^{-6}$), while the AI-service values
($\beta_d \sim 10^4$) are not derived from first principles.
The growth-rate observable $f\sigma_8(z)$ reproduces the shape of
$\varepsilon(z)$ at $r = 0.851$ for $z \le 5$ and identifies a secondary
structural feature at $z = 8.50$ consistent with the quadrupole term $F_q$.

The primary open questions are: a first-principles derivation of $\beta_d$
and $\beta_q$, a Lagrangian for MULTING, and the symmetry group for the
IDM isomer count.  Pending these, no strong conclusions about the physical
reality of the dipole force can be drawn from Table~A1 alone.

\begin{acknowledgments}
S.B.\ thanks T.J.\ Buckholtz for making the preprint publicly available and for
correspondence regarding the H(z) computation procedure.
This work used PDG 2024 constants, Planck 2018 cosmological parameters, and
the MCXC/XMM-Newton galaxy cluster catalogs.
\end{acknowledgments}

% ──────────────────────────────────────────────
\bibliography{refs}
% ──────────────────────────────────────────────

\end{document}
